QPLIB: A Library of Quadratic Programming Instances

### 2016-07-28 QPLIB-2.3.tex
changed notation as Ambros asked

Complete methods are often referred to as \emph{exact} in a large part of the mathematical optimization community. This nomenclature has to be used with care, as it implicitly makes assumptions on the underlying computational model that may not be acceptable in all cases. To see that, consider that, as already mentioned, QPs (more precisely, LIQ) are generally undecidable \cite{jeroslow}; and yet, there exists a general decision method for deciding feasibility of systems of polynomial equations and inequalities \cite{tarski-reals}, including the solution of LCQ with zero objective function. This apparent contradiction is due to the fact that the two statements refer to different computational models: the former is based on the Turing Machine (TM), whereas the latter is based on the Real RAM (RRAM) machine \cite{blum}. Due to the potentially infinite nature of exact real arithmetic computations, exact computations on the RRAM necessarily end up being approximate on the TM. Analogously, a complete method may reasonably be called ``exact'' on a RRAM; however, the computers we use in practice are more akin to TMs than RRAMs, and therefore 
calling \emph{exact} a solver that employs
%dubbing \emph{exact} a solver that employ 
floating point computations is, technically speaking, stretching the meaning of the word. However, because the term is well understood in the computational optimization community, in the following we shall loosen the distinction between complete and exact methods, with either properties intended to mean ``complete'' in the sense of \cite{neumaier}.

>>>>

Complete methods are often referred to as \emph{exact} in a large part of the mathematical optimization community. This nomenclature has to be used with care, as it implicitly makes assumptions on the underlying computational model that may not be acceptable in all cases. To see that, consider that, as already mentioned, QPs (more precisely, LIQ) are generally undecidable \cite{jeroslow}; and yet, there exists a general decision method for deciding feasibility of systems of polynomial equations and inequalities \cite{tarski-reals}, including the solution of LCQ with zero objective function. This apparent contradiction is due to the fact that the two statements refer to different computational models: the former is based on the Turing Machine (TM), whereas the latter is based on the Real RAM (RRAM) machine \cite{blum}. Due to the potentially infinite nature of exact real arithmetic computations, exact computations on the RRAM necessarily end up being approximate on the TM. Analogously, a complete method may reasonably be called ``exact'' on a RRAM; however, the computers we use in practice are more akin to TMs than RRAMs, and therefore calling \emph{exact} a solver that employs floating point computations is, technically speaking, stretching the meaning of the word. However, because the term is well understood in the computational optimization community, in the following we shall loosen the distinction between complete and exact methods, with either properties intended to mean ``complete'' in the sense of \cite{neumaier}.
